Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-05-16 GWLDCII.tex
What's up with 3.12?

@@

We claim that there is no repetition of propagators or vertices in this list; this will show that the process must eventually terminate. The claim is proved by induction.  The definition of $j_0$ gives that $j_0$ and $j_1$ are distinct and that $p_1$ and $p_2$ are distinct.  Now, suppose we have $p_r$ and $j_r$ with $I_i(p_r)=j_r$ and with $j_r\in J$.  Then there must exist a propagator $p_{r+1}$ with $J(p_{r+1}) = j_r$.  Since $J: \cP \longrightarrow [n]$ is injective and $j_r$ is not equal to any of the previous vertices $j_0, \dots, j_{r-1}$ by assumption, $p_{r+1}$ must be distinct from the previous propagators $p_1,\dots,p_r$.  Following the pattern, define $j_{r+1} = I_i(p_{r+1})$. Since $I_i: \cP \longrightarrow [n]$ is also injective and $p_{r+1}$ is distinct from the earlier $p_*$, it follows that $j_{r+1}$ is distinct from the other $j_s$ for $1\leq s\leq r$.  Finally, we have $j_{r+1}\neq j_0$ since $j_0\not\in I_i$ but $j_{r+1}\in I_i$.  This proves the claim.

>>>>

{\color{violet} This is a rephrasing of my theorem with Amat (Lemma 3.5 / Theorem 3.6): A set of vertices $V \subset [n]$ is independent if and only if it does not contain a $U \subsetneq V$ such that $|\Prop(U)| > |U|$, which is your injection condition. Is this second proof necessary? If so, should we at least cite that theorem?}

@@

We claim that there is no repetition of propagators or vertices in this list; this will show that the process must eventually terminate. The claim is proved by induction.  The definition of $j_0$ gives that $j_0$ and $j_1$ are distinct and that $p_1$ and $p_2$ are distinct.  Now, suppose we have $p_r$ and $j_r$ with $I_i(p_r)=j_r$, with $j_r$ distinct from all previous $j_*$ and with $j_r\in J$.  Then there must exist a propagator $p_{r+1}$ with $J(p_{r+1}) = j_r$.  Since $J: \cP \longrightarrow [n]$ is injective and $j_r$ is not equal to any of the previous vertices $j_0, \dots, j_{r-1}$ by assumption, $p_{r+1}$ must be distinct from the previous propagators $p_1,\dots,p_r$.  Following the pattern, define $j_{r+1} = I_i(p_{r+1})$. Since $I_i: \cP \longrightarrow [n]$ is also injective and $p_{r+1}$ is distinct from the earlier $p_*$, it follows that $j_{r+1}$ is distinct from the other $j_s$ for $1\leq s\leq r$.  Finally, we have $j_{r+1}\neq j_0$ since $j_0\not\in I_i$ but $j_{r+1}\in I_i$.  This proves the claim.
